Lattice Boltzmann study of mass transfer for complicated geometries

### 2012-02-04 Text/introduction.tex
Finished the draft.

\begin{document}
\maketitle
\begin{abstract}
This work presents a thorough procedure of how to determine the volumetric mass transfer
coefficient
in the context of lattice Boltzmann simulations. The novelty of this work lies in the establishing
a thorough procedure of how to measure the volumetric mass transfer coefficient in case of mass
sources to be comparable of the representative unit cell, which accounts for the inhomogenous
situation. By examining $5$ representative cases taken from microfluidics with the capillary number
from $Ca=0.1$ to $Ca=1$ the following relationship was established {\color{red} Give main findings
here}. The work is of use to people performing mass transfer numerical simulations.
\end{abstract}

@@

We chose to simulate mass transfer of the bubble train due to different reasons:
\begin{description}
\item[I] The gas holdup, i.e. the ratio of volume occupied by bubble to unit cell volume, is
non-negligible. Therefore, one cannot assume that the mass source is a point source which accounts
to the homogenous advection-diffusion equation with the mass source.  Therefore, there is a logical
mismatch: on one hand one needs to account the complicated geometry of the bubble and account for
all velocity pattern details, on the other hand one needs to mimic the continous picture which is
seen in experiments. One of the goals of this work is to establish certain criteria as how to
simulate such problems numerically with the help of the lattice Boltzmann method.
\item[II] For small capillary numbers as $Ca<0.7$ \cite{giavedoni-numerical} there is a vortex in
the reference frame moving with
the bubble, which  influences and improves the corresponding mass transfer.  For larger capillary
numbers there is no vortex and stremalines go around the bubble {\color{red} Give two pictures
with corresponding streamlines}. Thus, the problem is interesting because of different
hydrodynamic patterns depending on the capillary number which governs a number of experimental
parameters as the slug length, the film thickness and the existence of the vortex in front of the
bubble. There are some available
correlations in literature \cite{bercic-mass,kreutzer-overview}. One of the particular goal of
this work is to study mass transfer dependence on the completely different velocity patterns
depending on the capillary number $Ca$. 
\end{description}

@@

If one can assume that the mass point sources are distributed in the whole medium, then the mass accumulated in the unit volume $V=A \Delta x$ can be calculated as the difference of 
mass fluxes entering and leaving domain $U \bigl(C(x+\Delta x)-C(x)\bigr)$. We assume that the
source is a point source with the effective perimeter (area) $P$. The accumulated mass should be proportional
to the mass transfer coefficient:
\beq
U \bigl(C(x+\Delta x)-C(x)\bigr)=k_L P \bigl(\cstar-C(x)\bigr), 
\feq 
giving the same equation but only in the coordinate domain:
\beq
C(x)= \cstar \Bigl(1-\exp\bigl(-k_L a \frac{x}{U} \bigr)\Bigr).
\label{main:mass:transfer:expression} 
\feq

@@

We perform simulations in the frame moving with the bubble (velocity
$\ububble$), that the bubble position stands steady. The bubble velocity $\ububble$ is
different from the bulk velocity $\ugas+\uliq$. In this case we need to perform a coordinate $x$
variable change:
\beqal
\label{theor:average:concentration:time}
&x(t)=\ububble t\\
&C(x)=\cstar \Bigl(1-\exp\bigl(-\vol \frac{x}{\ugas+\uliq}\bigr)\Bigr)\\
&C(t)=\cstar \Bigl(1-\exp\bigl(-\vol\, t \frac{\ububble}{\ugas+\uliq}\bigr)\Bigr).
\feqal
Therefore, one can obtain the volumetric mass transfer coefficient through the concentration:
\beqal
&\vol\, t \frac{\ububble}{\ugas+\uliq}=\ln \frac{\cstar}{\cstar-C(t)}\\
&\volnondim=\frac{\lunit}{\ububble t}\ln \frac{\cstar}{\cstar-C(t)},
\feqal
where the parameter $\vol \frac{\lunit}{\ugas+\uliq}$ is non-dimensional. One can also measure the
volumetric mass transfer coefficient from concentrations given at times $t_1$ and $t_2$:
\beq
\label{theor:continuous:mass:transfer}
\volnondim=\frac{\lunit}{\ububble
(t_2-t_1)}\ln\frac{C^{*}-C(t_1)}{C^{*}-C(t_2)}.
\feq
Expressions (\ref{theor:average:concentration:time}) and (\ref{theor:continuous:mass:transfer}) are
the cornerstones of the present work. The main questions arisen in the present work are to define
$C(t)$ and  the boundary conditions to produce a proper volumetric mass transfer coefficient
$\vol$.

Three possible scenarios of conducting numerical simulations are possible: 
\begin{enumerate}
\item As far as the hydrodynamic flow is periodic, one can make an assumption of the same boundary
conditions applied to the tracer concentration. Therefore, only one unit cell is simulated with
periodic boundary conditions, see Fig. \ref{fig:benchmark}. As well, no tracer leaves a
domain. The situation resembles a situation for the plug flow, where no tracer can leave a unit
domain. We expect such a situation happening for small Capillary numbers $Ca<0.1$, where the film
is thin and saturates fast with the tracer. Though easier to implement, it rises certain critisism
towards the inlet concentration to be equal to the outlet concentration. In the continuous
formulation there is the concentration difference between inlet and outlet involving the volumetric
mass transfer coefficient:
\beq
\volnondim=\ln\frac{\cstar-\cinlet}{\cstar-\coutlet}.
\feq
The concentration $C(t)$ required for calculation the volumetric mass transfer coefficient, Eq.
(\ref{theor:average:concentration:time}), can be taken as the average concentration in the domain:
\beq
\label{average:concentration:definition}
C(t)=\frac{\int_{liquid}{C \mathrm{d}V}}{\int{\mathrm{d}V}}.
\feq
\begin{figure}[htb!]
\includegraphics[width=\textwidth]{Figures/benchmark_middle.eps}\\
\caption{The two-dimensional benchmarks for the  the mass transfer
coefficient (bottom) for the bubble located near the entrance (top) and at the middle of the domain
(bottom). \label{fig:benchmark}}
\end{figure}
\item The second approach is the same as the first one but the concentration is taken as in
\cite{vanbaten-circular}. The characteristic concentration is taken as the inlet/outlet
concentration:
\beqal
&\cinlet=\frac{\int{U(y) C(0,y,t) \mathrm{d}y}}{\int{U(0,y) \mathrm{d}y}}\\
&\coutlet=\frac{\int{U(y) C(\lunit,y,t) \mathrm{d}y}}{\int{U(\lunit,y) \mathrm{d}y}}\\
&\cinlet=\coutlet.
\feqal
Therefore the assumptions  of this approach is that the difference between inlet and outlet is not
considerably large and the tracer is well mixed in the slug.

\item
The approach of \citet{vanbaten-circular} is taken. Periodic boundary conditions were used. By the
definition the mass transfer coefficient is
proportional to the gain of the mass in the system divided by the concentration difference
multiplied on the surface area:
\beq
\vol=\frac{\dot{m}}{P \Delta C}\frac{P}{V}=\frac{\dot{m}}{V (\cstar-C(t))},
\feq
where mass difference in the domain can be calculated as:
\beq
\dot{m}=\frac{m_2-m_1}{t_2-t_1}=\frac{\int_{liq}{C(t_2)\mathrm{d}V}-\int_liq{C(t_1)\mathrm{d}V}}{
t_2-t_1 } .
\feq
In the approach of \citet{vanbaten-circular} the inlet and outlet concentrations were taken as the
characteristic concentration $C(t)$.

\item 
The approach of the opened boundaries was examined, see Fig. \ref{fig:benchmark:jos}. At the inlet
and outlet boundaries the diffusion flux was imposed to be zero, $\frac{\partial C}{\partial x}=0$.
The characteristic concentration was taken as the average concentration in the whole domain.
\begin{figure}
\includegraphics[width=\textwidth]{Figures/benchmark_jos.eps}
\caption{The numerical mass transfer benchmark with open boundaries. The mass transfer is
calculated according to Eq. \ref{theor:average:concentration:time} with the characteristic
concentration accoring to Eq. \ref{average:concentration:definition}. \label{fig:benchmark:jos}}
\end{figure}

\item 
The last approach to be examined in this paper is the approach of the simulation of a lot of unit
volumes, see Fig. \ref{big:benchmar:alot}. This situation corresponds to the simulation of the
bubble train head, after injecting to the pipe and travelling along the pipe. The argument here is
that behind a certain number of the bubble train head, the influence of the boundaries will be
diminished. Thus, the average concentration in time will be governed by Eq.
\ref{theor:continuous:mass:transfer}. This simulation statement is of most correspondence to
experiments and should give right answer. However, one of the
disadvantages is to simulate a certain number of unit cells, thus increasing a computational
complexity.
\begin{figure}[htb!]
\includegraphics[width=\textwidth]{Figures/benchmark_alot.eps}\\
\caption{Benchmark for a lot of units. \label{fig:benchmark:alot}}
\end{figure}
\end{enumerate}

@@

\subsection{Parabolic profile with the velocity zero gradient at the wall}
The problem is defined in terms of PDE as follows: 
\beq
\begin{aligned}
&\frac{\partial C}{\partial x} U(y)=D\frac{\partial^2 C}{\partial y^2}\\
&C(0,y)=C_0,\, C(x,0)=\cstar,\, \frac{\partial C}{\partial y }(x,\delta)=0\\
&U(y)=U_0 \Bigl(\frac{y}{\delta}\Bigr)^2.
\end{aligned}
\feq
The procedure to solve this PDE is presented in Appendix \ref{appendix:zero:gradient}:
\beq
\label{analytical:solution:zero:gradient}
\begin{aligned}
&C(x,y)=\cstar+\sum_{m}{C_m
\sqrt{\frac{y}{H}}J_{\frac{1}{4}}\Bigl(\frac{m^2}{2}\frac{y^2}{H^2}\Bigr)\exp\Bigl(-\frac{m^4}{Pe}
\frac { x }{H}\Bigr)}\\
&C_m = (C_0-\cstar \frac{\int_{\xi=0}^{1}{\xi^{5/2} J_{\frac{1}{4}}\Bigl(\frac{m^2
\xi^2}{2}\Bigr)\mathrm{d}\xi}}{\int_{\xi=0}^{1}{\xi^3 J_{\frac{1}{4}}^2\Bigl(\frac{m^2
\xi^2}{2}\Bigr)\mathrm{d}\xi}}
\end{aligned}
\feq
Fig. \ref{fig:parabolic:zero:gradient} shows the steady-state contours comparison between the
analytical and the simulation with the Anti Bounce-Back conditions used to impose constant
concentrations at the wall $\cstar=1$ and the inlet $C_0=0$. The grid used in the simulation is
$80\times1600$. Parameter $\omegaminus=1.8$ implies the diffusion coefficient to be
$D=\frac{1}{3}\Bigl(\frac{1}{\omega}-\frac{1}{2}\Bigr)=0.0185$.  
\begin{figure}[htb!]
\includegraphics[width=\textwidth]{Figures/parabolic_profile_zero_gradient_comparison.eps}
\caption{Comparison with the analytical concentration contours, Eq.
(\ref{analytical:solution:zero:gradient}), for the diffusion coefficient $D=0.0185$. Simulation was
performed on grid $80\times 1600$. The constant concentration is imposed with the
anti bounce-back conditions, Eq.\ref{antibb}. \label{fig:parabolic:zero:gradient}}
\end{figure}

\subsection{Poiseulle velocity parabolic profile}
The problem we want to address can be formulated through the following PDE:
\beq
\begin{aligned}
&\frac{\partial C}{\partial x} U(y)=D\frac{\partial^2 C}{\partial y^2}\\
&C(0,y)=0,\, C(x,\pm \delta)=\cstar,\, \frac{\partial C}{\partial y }(x,0)=0\\
&U(y)=U_0 \Bigl(1-\bigl(\frac{y}{\delta}\bigr)^2\Bigr)
\end{aligned}
\feq
The procedure to solve this problem is presented in Appendix \ref{appendix:poiseuille} which yields
the final solution as:
\begin{equation}
C=\cstar-\cstar \sum_{m=0}{C_m e^{-m^4 \frac{x}{\delta}\frac{1}{Pe}} e^{-m^2
y^2/(2\delta^2)}{_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2 \frac{y^2}{\delta^2}\Bigr)},
\end{equation}
where coefficients $C_m$ are taken from Eq. (\ref{coeff:series:parabolic:profile}). The comparison
between contours of analytical and simulation results is presented in Fig.
\ref{fig:parabolic:comparison}. Parameters were taken the same as in the previous case: the
diffusion $D=0.0185$, the grid dimension is $80\times1600$. 
\begin{figure}[htb!]
\includegraphics[width=\textwidth]{Figures/parabolic_profile_comparison.eps}
\caption{Comparison between the analytical concentration contours and simulations with pressure
anti bounce-back conditions, Eq. (\ref{antibb}). The parameters were
taken as $D=0.0185$ and grid $80\times1600$. \label{fig:parabolic:comparison}}
\end{figure}

@@

Given all the considerations above, one needs to approach the mass transfer in the following
steps:
\begin{description}
 \item[Flow field] Given the capillary number $Ca$, one needs to obtain hydrodynamic fields around
the bubble using the binary liquid lattice Boltzmann model according to work
\cite{kuzmin-binary2d}. Periodic boundary conditions are used. The grid used in this work is
$202\times 3000$ which corresponds to fluid domain size $200\times3000$. The grid resolution is
taken to insure grid
independency of results.  
 \item[Bubble reference frame] Once the hydrodynamics is resolved, the mass transfer simulations
are conducted in the moving reference frame with the bubble. Then the bubble stands still and the
flow is coming around the
bubble. We impose a steady concentration of the trace on the surface
of the bubble with the anti bounce-back condition, Eq. (\ref{antibb}).
 \item[Velocity improvement] Due to necessity to increase velocity one can scale the velocity to
perform fast simulations, one needs to improve velocity. This issue arises because of the
multiphase model used in simulations.The binary liquid lattice Boltzmann model is the diffusive
interface model. Thus, the
transition between gas and liquid is the continuous function. We obtain the bubble shape according
to the phase indicator $\phi$ as used in \cite{kuzmin-binary2d}, say $\phi<0$. The velocity of the
bubble is calculated as the bubble tip velocity. Because of the highly non-linear diffusive
interface model the shape of the bubble is determined within accuracy of one grid node, as well
there is the error in determination in the bubble velocity. Though these errors are small, however
there is small non-zero velocity component pointing to the bubble in some places, see Fig. 8 in
\cite{kuzmin-binary2d} where some streamlines are penetrating a bubble surface a bit.
This small velocity is amplified upon the velocity scaling and is inconsistent with the
advection-diffusion equation.

@@

\item[Mass transfer] After improved velocity profiles are obtained one can perform any mass
transfer simulations with different boundary conditions as covered in Section \ref{section:cases}.
For this purpose one needs to match the Peclet number $Pe$ from experiments. Note that we
specifically separated the hydrodynamic problem from the mass transfer problem. When one wants to
solve these simultaneous problems, then one needs to match all the non-dimensional parameters, as
the capillary number (viscous forces over surface tension), the Schmidt number (viscous diffusion
rate over mass diffusion rate), the Peclet number (convection over diffusion) and the Sherwood
number (convection mass transfer over diffusion mass transfer):
\begin{equation}
\begin{aligned}
&Ca=\frac{\ububble \mu_{\mathrm{liq}}}{\gamma}\\
&Pe=\frac{\ububble L}{D}\\
&Sh=\frac{K L}{D}\\
&Sc=\frac{\nu}{D}.
\end{aligned}
\end{equation}
\end{description}

\section{Keeping Peclet}
This section addresses the performance of the simulations. The ulimate goal is to increase
velocity at least by several orders while keeping dimensionless parameters the same. Increasing
velocity can result in simulations of a lot of unit cells required for continuous picture
representation.

>>>>

\begin{document}
\maketitle
\begin{abstract}
This work presents a thorough procedure of how to determine the volumetric mass transfer
coefficient
in the context of lattice Boltzmann simulations. The novelty of this work lies in the establishing
a thorough procedure of how to measure the volumetric mass transfer coefficient in case of mass
sources to be comparable of the representative unit cell, which accounts for the inhomogenous
situation. The strategies of how to speed up simulations, what the boundaries conditions are
thoroughly examined. Overall, all methods are consistent between each other as soon as the averaged
domain concentration is taken as the characteristic concentration. Though more difficult to setup
simulations with a few unit cells can give additional information about how well the liquid slug is
mixed. The work is of use to people performing mass transfer numerical simulations within the
lattice Boltzmann context.
\end{abstract}

@@

We chose to simulate mass transfer of the bubble train due to different reasons:
\begin{description}
\item[I] The gas holdup, i.e. the ratio of volume occupied by bubble to unit cell volume, is
non-negligible. Therefore, one cannot assume that the mass source is a point source which accounts
to the homogenous advection-diffusion equation with the mass source.  Therefore, there is a logical
mismatch: on one hand one needs to account the complicated geometry of the bubble and account for
all velocity pattern details, on the other hand one needs to mimic the continous picture which is
seen in experiments. One of the goals of this work is to establish certain criteria as how to
simulate such problems numerically with the help of the lattice Boltzmann method.
\item[II] For small capillary numbers as $Ca<0.7$ \cite{giavedoni-numerical} there is a vortex in
the reference frame moving with
the bubble, which  influences and improves the corresponding mass transfer.  For larger capillary
numbers there is no vortex and stremalines go around the bubble, see Fig.
\ref{fig:streamlines:tweaked:velocity}. Thus, the problem is interesting because of different
hydrodynamic patterns depending on the capillary number which governs a number of experimental
parameters as the slug length, the film thickness and the existence of the vortex in front of the
bubble. There are some available
correlations in literature \cite{bercic-mass,kreutzer-overview}. One of the particular goal of
this work is to study mass transfer dependence on the completely different velocity patterns
depending on the capillary number $Ca$. 
\end{description}

@@

If one can assume that the mass point sources are distributed in the whole medium, then the mass accumulated in the unit volume $V=A \Delta x$ can be calculated as the difference of 
mass fluxes entering and leaving domain $U \bigl(C(x+\Delta x)-C(x)\bigr)$. We assume that the
source is a point source with the effective perimeter (area) $P$. The accumulated mass should be proportional
to the mass transfer coefficient:
\beq
U \bigl(C(x+\Delta x)-C(x)\bigr)=k_L P \bigl(\cstar-C(x)\bigr), 
\feq 
giving the same equation but only in the coordinate domain:
\beq
\label{concentration:domain:coordinate}
C(x)= \cstar \Bigl(1-\exp\bigl(-k_L a \frac{x}{U} \bigr)\Bigr).
\label{main:mass:transfer:expression} 
\feq

@@

We perform simulations in the frame moving with the bubble (velocity
$\ububble$), that the bubble position stands steady. The bubble velocity $\ububble$ is
different from the bulk velocity $\ugas+\uliq$. In this case we need to perform a coordinate $x$
variable change:
\beqal
\label{theor:average:concentration:time}
&x(t)=\ububble t\\
&C(x)=\cstar \Bigl(1-\exp\bigl(-\vol \frac{x}{\ugas+\uliq}\bigr)\Bigr)\\
&C(t)=\cstar \Bigl(1-\exp\bigl(-\vol\, t \frac{\ububble}{\ugas+\uliq}\bigr)\Bigr).
\feqal
Therefore, one can obtain the volumetric mass transfer coefficient through the concentration:
\beqal
\label{theor:one:concentration:time}
&\vol\, t \frac{\ububble}{\ugas+\uliq}=\ln \frac{\cstar}{\cstar-C(t)}\\
&\volnondim=\frac{\lunit}{\ububble t}\ln \frac{\cstar}{\cstar-C(t)},
\feqal
where the parameter $\vol \frac{\lunit}{\ugas+\uliq}$ is non-dimensional. One can also measure the
volumetric mass transfer coefficient from concentrations given at times $t_1$ and $t_2$:
\beq
\label{theor:continuous:mass:transfer}
\volnondim=\frac{\lunit}{\ububble
(t_2-t_1)}\ln\frac{C^{*}-C(t_1)}{C^{*}-C(t_2)}.
\feq
Expressions (\ref{theor:average:concentration:time}) and (\ref{theor:continuous:mass:transfer}) are
the cornerstones of the present work. The main questions arisen in the present work are to define
$C(t)$ and  the boundary conditions to produce a proper volumetric mass transfer coefficient
$\vol$.

Three possible scenarios of conducting numerical simulations are possible: 
\begin{enumerate}
\item As far as the hydrodynamic flow is periodic, one can make an assumption of the same boundary
conditions applied to the tracer concentration. Therefore, only one unit cell is simulated with
periodic boundary conditions, see Fig. \ref{fig:benchmark}. As well, no tracer leaves a
domain. The situation resembles a situation for the plug flow, where no tracer can leave a unit
domain. We expect such a situation happening for small Capillary numbers $Ca<0.1$, where the film
is thin and saturates fast with the tracer. Though easier to implement, it rises certain critisism
towards the inlet concentration to be equal to the outlet concentration. In the continuous
formulation there is the concentration difference between inlet and outlet involving the volumetric
mass transfer coefficient:
\beq
\volnondim=\ln\frac{\cstar-\cinlet}{\cstar-\coutlet}.
\feq
The concentration $C(t)$ required for calculation the volumetric mass transfer coefficient, Eq.
\ref{theor:one:concentration:time}, can be taken as the average concentration in the domain:
\beq
\label{average:concentration:definition}
C(t)=\frac{\int_{liquid}{C \mathrm{d}V}}{\int{\mathrm{d}V}}.
\feq
\begin{figure}[htb!]
\includegraphics[width=\textwidth]{Figures/benchmark_middle.eps}\\
\caption{The two-dimensional benchmarks for the  the mass transfer
coefficient (bottom) for the bubble located near the entrance (top) and at the middle of the domain
(bottom). \label{fig:benchmark}}
\end{figure}
\item The second approach is the same as the first one but the concentration is taken as in
\cite{vanbaten-circular}. The characteristic concentration is taken as the inlet/outlet
concentration:
\beqal
&\cinlet=\frac{\int{U(y) C(0,y,t) \mathrm{d}y}}{\int{U(0,y) \mathrm{d}y}}\\
&\coutlet=\frac{\int{U(y) C(\lunit,y,t) \mathrm{d}y}}{\int{U(\lunit,y) \mathrm{d}y}}\\
&\cinlet=\coutlet.
\feqal
Therefore the assumptions  of this approach is that the difference between inlet and outlet is not
considerably large and the tracer is well mixed in the slug.

\item
The approach of \citet{vanbaten-circular} is taken. Periodic boundary conditions were used. By the
definition the mass transfer coefficient is
proportional to the gain of the mass in the system divided by the concentration difference
multiplied on the surface area:
\beq
\vol=\frac{\dot{m}}{P \Delta C}\frac{P}{V}=\frac{\dot{m}}{V (\cstar-C(t))},
\feq
where mass difference in the domain can be calculated as:
\beq
\dot{m}=\frac{m_2-m_1}{t_2-t_1}=\frac{\int_{liq}{C(t_2)\mathrm{d}V}-\int_{liq}{C(t_1)\mathrm{d}V}}{
t_2-t_1 } .
\feq
In the approach of \citet{vanbaten-circular} the inlet and outlet concentrations were taken as the
characteristic concentration $C(t)$.

%\item 
%The approach of the opened boundaries was examined, see Fig. \ref{fig:benchmark:jos}. At the inlet
%and outlet boundaries the diffusion flux was imposed to be zero, $\frac{\partial C}{\partial x}=0$.
%The characteristic concentration was taken as the average concentration in the whole domain.
%\begin{figure}
%\includegraphics[width=\textwidth]{Figures/benchmark_jos.eps}
%\caption{The numerical mass transfer benchmark with open boundaries. The mass transfer is
%calculated according to Eq. \ref{theor:average:concentration:time} with the characteristic
%concentration accoring to Eq. \ref{average:concentration:definition}. \label{fig:benchmark:jos}}
%\end{figure}

\item 
The last approach to be examined in this paper is the approach of the simulation of a lot of unit
volumes, see Fig. \ref{fig:benchmark:alot}. This situation corresponds to the simulation of the
bubble train head, after injecting to the pipe and travelling along the pipe. The argument here is
that behind a certain number of the bubble train head, the influence of the boundaries will be
diminished. Thus, the average concentration in time will be governed by Eq.
\ref{theor:continuous:mass:transfer}. This simulation statement is of most correspondence to
experiments and should give right answer. However, one of the
disadvantages is to simulate a certain number of unit cells, thus increasing a computational
complexity.
\begin{figure}[htb!]
\includegraphics[width=\textwidth]{Figures/benchmark_alot.eps}\\
\caption{Benchmark for a lot of units. \label{fig:benchmark:alot}}
\end{figure}
\end{enumerate}

@@

\subsection{Parabolic profile with the velocity zero gradient at the wall}
The problem is defined in terms of PDE as follows: 
\beq
\begin{aligned}
&\frac{\partial C}{\partial x} U(y)=D\frac{\partial^2 C}{\partial y^2}\\
&C(0,y)=C_0,\, C(x,0)=\cstar,\, \frac{\partial C}{\partial y }(x,\delta)=0\\
&U(y)=U_0 \Bigl(\frac{y}{\delta}\Bigr)^2.
\end{aligned}
\feq
The procedure to solve this PDE is presented in Appendix \ref{appendix:zero:gradient}:
\beq
\label{analytical:solution:zero:gradient}
\begin{aligned}
&C(x,y)=\cstar+\sum_{m}{C_m
\sqrt{\frac{y}{H}}J_{\frac{1}{4}}\Bigl(\frac{m^2}{2}\frac{y^2}{H^2}\Bigr)\exp\Bigl(-\frac{m^4}{Pe}
\frac { x }{H}\Bigr)}\\
&C_m = (C_0-\cstar \frac{\int_{\xi=0}^{1}{\xi^{5/2} J_{\frac{1}{4}}\Bigl(\frac{m^2
\xi^2}{2}\Bigr)\mathrm{d}\xi}}{\int_{\xi=0}^{1}{\xi^3 J_{\frac{1}{4}}^2\Bigl(\frac{m^2
\xi^2}{2}\Bigr)\mathrm{d}\xi}}
\end{aligned}
\feq
Fig. \ref{fig:parabolic:zero:gradient} shows the steady-state contours comparison between the
analytical and the simulation with the Anti Bounce-Back conditions used to impose constant
concentrations at the wall $\cstar=1$ and the inlet $C_0=0$. The grid used in the simulation is
$80\times1600$. Parameter $\omegaminus=1.8$ implies the diffusion coefficient to be
$D=\frac{1}{3}\Bigl(\frac{1}{\omega}-\frac{1}{2}\Bigr)=0.0185$.  
\begin{figure}[htb!]
\includegraphics[width=\textwidth]{Figures/parabolic_profile_zero_gradient_comparison.eps}
\caption{Comparison with the analytical concentration contours, Eq.
\ref{analytical:solution:zero:gradient}, for the diffusion coefficient $D=0.0185$. Simulation was
performed on grid $80\times 1600$. The constant concentration is imposed with the
anti bounce-back conditions, Eq. \ref{antibb}. \label{fig:parabolic:zero:gradient}}
\end{figure}

\subsection{Poiseulle velocity parabolic profile}
The problem we want to address can be formulated through the following PDE:
\beq
\begin{aligned}
&\frac{\partial C}{\partial x} U(y)=D\frac{\partial^2 C}{\partial y^2}\\
&C(0,y)=0,\, C(x,\pm \delta)=\cstar,\, \frac{\partial C}{\partial y }(x,0)=0\\
&U(y)=U_0 \Bigl(1-\bigl(\frac{y}{\delta}\bigr)^2\Bigr)
\end{aligned}
\feq
The procedure to solve this problem is presented in Appendix \ref{appendix:poiseuille} which yields
the final solution as:
\begin{equation}
C=\cstar-\cstar \sum_{m=0}{C_m e^{-m^4 \frac{x}{\delta}\frac{1}{Pe}} e^{-m^2
y^2/(2\delta^2)}{_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2 \frac{y^2}{\delta^2}\Bigr)},
\end{equation}
where coefficients $C_m$ are taken from Eq. \ref{coeff:series:parabolic:profile}. The comparison
between contours of analytical and simulation results is presented in Fig.
\ref{fig:parabolic:comparison}. Parameters were taken the same as in the previous case: the
diffusion $D=0.0185$, the grid dimension is $80\times1600$. 
\begin{figure}[htb!]
\includegraphics[width=\textwidth]{Figures/parabolic_profile_comparison.eps}
\caption{Comparison between the analytical concentration contours and simulations with pressure
anti bounce-back conditions, Eq. \ref{antibb}. The parameters were
taken as $D=0.0185$ and grid $80\times1600$. \label{fig:parabolic:comparison}}
\end{figure}

@@

Given all the considerations above, one needs to approach the mass transfer in the following
steps:
\begin{description}
 \item[Flow field] Given the capillary number $Ca$, one needs to obtain hydrodynamic fields around
the bubble using the binary liquid lattice Boltzmann model according to work
\cite{kuzmin-binary2d}. Periodic boundary conditions are used. The grid used in this work is
$202\times 3000$ which corresponds to fluid domain size $200\times3000$. The grid resolution is
taken to insure grid
independency of results.  
 \item[Bubble reference frame] Once the hydrodynamics is resolved, the mass transfer simulations
are conducted in the moving reference frame with the bubble. Then the bubble stands still and the
flow is coming around the
bubble. We impose a steady concentration of the trace on the surface
of the bubble with the anti bounce-back condition, Eq. \ref{antibb}.
 \item[Velocity improvement] Due to necessity to increase velocity one can scale the velocity to
perform fast simulations, one needs to improve velocity. This issue arises because of the
multiphase model used in simulations.The binary liquid lattice Boltzmann model is the diffusive
interface model. Thus, the
transition between gas and liquid is the continuous function. We obtain the bubble shape according
to the phase indicator $\phi$ as used in \cite{kuzmin-binary2d}, say $\phi<0$. The velocity of the
bubble is calculated as the bubble tip velocity. Because of the highly non-linear diffusive
interface model the shape of the bubble is determined within accuracy of one grid node, as well
there is the error in determination in the bubble velocity. Though these errors are small, however
there is small non-zero velocity component pointing to the bubble in some places, see Fig. 8 in
\cite{kuzmin-binary2d} where some streamlines are penetrating a bubble surface a bit.
This small velocity is amplified upon the velocity scaling and is inconsistent with the
advection-diffusion equation.

@@

\item[Mass transfer] After improved velocity profiles are obtained one can perform any mass
transfer simulations with different boundary conditions as covered in Section \ref{section:cases}.
For this purpose one needs to match the Peclet number $Pe$ from experiments. Note that we
specifically separated the hydrodynamic problem from the mass transfer problem. When one wants to
solve these simultaneous problems, then one needs to match all the non-dimensional parameters, as
the capillary number (viscous forces over surface tension), the Schmidt number (viscous diffusion
rate over mass diffusion rate), the Peclet number (convection over diffusion), the Reynolds number
(inertia over viscous forces) and the Sherwood
number (convection mass transfer over diffusion mass transfer):
\begin{equation}
\begin{aligned}
&Re=\frac{\ububble L}{\nu_{\mathrm{liq}}},&&Ca=\frac{\ububble \mu_{\mathrm{liq}}}{\gamma}\\
&Pe=\frac{\ububble L}{D},&&Sh=\frac{K L}{D}\\
&Sc=\frac{\nu_{\mathrm{liq}}}{D}.&&
\end{aligned}
\end{equation}
\end{description}

\section{Results}
This section covers simulation results. We first examine the possibility to increase the fluid
velocity while keeping the Peclet number the same. After that we will examine the periodic boundary
conditions for $5$ capillary cases, open boundary simulations, and finally we will examine many
cells simulations for two representative cases velocity patterns, as $Ca=0.0907$ and $Ca=1.04$
(see Fig. \ref{fig:streamlines:tweaked:velocity}).

\subsection{Keeping Peclet}
\label{section:keeping:peclet}
This section addresses the performance of the simulations. The ulimate goal is to increase
velocity at least by several orders while keeping dimensionless parameters the same to speed up
simulations. Increasing velocity can also help to resolve a lot of unit cells to represent a
continous picture.
